Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-19 2016-Weak-FH-Bisim/WeakBisim.tex
over skype

We denote $y\gets e$ a substitution. The application of the substitution is denoted
$\subst{y\gets e}$, the operation replaces in a term all occurrences 
of the variable $y$ by the expression $e$ (note that the absence of binders makes this operation 
trivial). 
We use \ERIC{sets of assignments of the form $x_i:=e_i$}, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner. $\otimes$ is the composition operator on substitutions: $(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$

@@

\subsection{Open Automata}
 Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values). Formaly, each state of an OA has a set of \emph{state variables}, and all state variable sets are disjoint.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]\label{def:OT}
	\label{def:OpenTransitions}
	An \emph{open transition} (OT) over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J'}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action of this open transition.
        We call \emph{source variables} of an OT the union of all variables
        in the different terms
        $\beta_j$ and $\alpha$, and the state variables of $s$.
        \Pred\ is a predicate over the source variables. \Post\ is a set of 
	\ERIC{assignments that are effective \emph{after the open transition}}, they are
        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
	where $x_k$ are state variables of $s'$, and $e_k$ are expressions
        over the source variables. Open transitions are identified
        modulo logical equivalence on their predicate. 
\end{definition}

@@

         For any of these, apply again WT3, using the central \texttt{q-recv(ec)} transition as $\alpha$, and you get:
      $\openrule
         {\gamma=\{\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
			\subst{ec\gets ec+n} }
         {s \OTWeakarrow {\texttt{q-recv(ec)}\subst{ec\gets ec+n}} s'}$

>>>>

We denote $y\gets e$ a substitution. The application of the substitution is denoted
$\subst{y\gets e}$, the operation replaces in a term all occurrences 
of the variable $y$ by the expression $e$ (note that the absence of binders makes this operation 
trivial). 
We use sets of assignments of the form $x_i:=e_i$, ranged over by $\Post$; $\subst{\Post}$ is the substitution that applies all the substitutions defined by $\Post$ in a parallel manner. $\otimes$ is the composition operator on substitutions: $(x_k\gets e_k)^{k\in K}\shortotimes \Post =  (x_k\gets e_k\subst{\Post})^{k\in K}$

@@

\subsection{Open Automata}
 Open automata (OA) are not composition structures but they are made of transitions that are dependent of the actions of the holes, and they can reason on variables (potentially with only symbolic values). Formaly, each state of an OA has a set of \emph{state variables}, and all state variable sets are disjoint.
%\TODO{adopt a uniform notation for open transitions, almost each instance has a 
%different 
%notation! I suggest p,l,pr,po using \{\} for p,l,po as they are sets}
\begin{definition}[Open transitions]\label{def:OT}
	\label{def:OpenTransitions}
	An \emph{open transition} (OT) over a
	set $J$ of holes with sorts $\Sort_j^{j\in J}$ and a set of states $\mathcal{S}$ is 
	a structure of the form:	
	\begin{mathpar}
	\openrule
	{	\beta_j^{j\in J'}, \Pred, \Post}
	{s \OTarrow {\alpha}s'}
	\end{mathpar}
	Where $J'\subseteq J$, $s, s'\in\mathcal{S}$ and $\beta_j$
        is a transition of the hole $j$, with $\beta_j\in\Sort_j$. $\alpha$ is an action 
        label denoting the resulting action of this open transition.
        We call \emph{source variables} of an OT the union of all variables
        in the different terms
        $\beta_j$ and $\alpha$, and the state variables of $s$.
        \Pred\ is a predicate over the source variables. \Post\ is a set of 
	assignments that are effective \emph{after the open transition}, they are
        represented as a substitution of the form $({x_k\gets e_k})^{k\in K}$ 
	where $x_k$ are state variables of $s'$, and $e_k$ are expressions
        over the source variables. Open transitions are identified
        modulo logical equivalence on their predicate. 
\end{definition}

@@

         For any of these, apply again WT3, using the central \texttt{q-recv(ec)} transition as $\alpha$, and you get:
      $\openrule
         {\{Q\mapsto\texttt{q-revc(ec)}\subst{ec\gets ec+n}\}, True,
			\subst{ec\gets ec+n} }
         {s \OTWeakarrow {\texttt{q-recv(ec)}\subst{ec\gets ec+n}} s'}$
